---
title: ""
output: word_document
params:
  projectName: "ProjectName"
  stationMetadata: "NADF"
  weatherDataFrame: "NADF"
  prescriptionRangesDataFrame: "NADF"
  prescriptionDataFrame: "NADF"
---

```{r setup, include = FALSE, echo = TRUE}
library("leaflet")

stationMetadataLocal <- params$stationMetadata
mapLocal <- params$MapLocation
prescriptionParams <- params$prescriptionRangesDataFrame

widthPlots <- 8
heightPlots <- 2 * length(unique(wx_df$Year))
```

# `r params$projectName`

## Station Metadata

Station used for the analysis:

Station: `r stationMetadataLocal$STATION$NAME`  
Station ID: `r stationMetadataLocal$STATION$STID`  
Elevation: `r stationMetadataLocal$STATION$ELEVATION`  
Lat / Long: `r paste(stationMetadataLocal$STATION$LATITUDE, stationMetadataLocal$STATION$LONGITUDE)`  
County, State: `r paste(stationMetadataLocal$STATION$COUNTY,", ",stationMetadataLocal$STATION$STATE, sep = "")`  
NWS Fire Weather Zone: `r stationMetadataLocal$STATION$NWSFIREZONE`  

## Prescription

### Prescription Parameters

Months: `r prescriptionParams$Month.Low` - `r prescriptionParams$Month.High`  
Hours: `r prescriptionParams$Hour.Low` - `r prescriptionParams$Hour.High`  

Temperature (F): `r prescriptionParams$Temp.Low` - `r prescriptionParams$Temp.High`  
Relative Humidity %: `r prescriptionParams$RH.Low` - `r prescriptionParams$RH.High`  
1 hr Fuel Moisture (%): `r prescriptionParams$FM1.Low` - `r prescriptionParams$FM1.High`  
10 hr Fuel Moisture (%): `r prescriptionParams$FM10.Low` - `r prescriptionParams$FM10.High`  
Wind Speed (mph): `r prescriptionParams$Wind.Low` - `r prescriptionParams$Wind.High`  
Wind Directions: `r prescriptionParams$WindDirections`

### Prescription Windows

```{r windowPlot, include = TRUE, echo = FALSE, warning = FALSE, message = FALSE, dpi = 95, fig.width = widthPlots, fig.height = 6}

hoursLabel <- c("0000","0100","0200","0300","0400","0500","0600","0700","0800","0900","1000","1100", "1200","1300","1400","1500","1600","1700","1800","1900","2000","2100","2200","2300")

monthLabel <- c("JAN","FEB","MAR","APR","MAY","JUN","JUL","AUG","SEP","OCT","NOV","DEC")
  
lims_dt <-
  as.POSIXct(strptime(c(min(filter(combinedWx, Conditions %in% "Not Matching")$hms),
                        max(filter(combinedWx, Conditions %in% "Not Matching")$hms)),
                      format = "%Y-%m-%d %H:%M"))

lims_d <- as.Date(c(min(wx_df$DayOfYear),max(wx_df$DayOfYear)))
  

rh_sub_Plot <- ggplot(data = filter(combinedWx, Conditions %in% "In Prescription"), aes(x = Month, y = Hour))+
  annotate("rect",
           xmin = min(filter(combinedWx, Conditions %in% "Window")$Month),
           xmax = max(filter(combinedWx, Conditions %in% "Window")$Month),
           ymin = min(filter(combinedWx, Conditions %in% "Window")$Hour),
           ymax = max(filter(combinedWx, Conditions %in% "Window")$Hour),
           alpha = .2, color = "green")+
  stat_density_2d(aes(fill = ..level..),
                  geom = "polygon", alpha = 0.1)+
  scale_fill_continuous("Probability Density", guide = FALSE)+
  geom_count(fill = "red", alpha = .5, pch=21)+
  scale_size_area(name = "Number of Hours In Prescription",
                  max_size = 7,
                  breaks = c(seq(1,7,1)))+
  scale_x_continuous("Months",
                     breaks = seq(1,12,1),
                     labels = monthLabel,
                     limits = c(0.5,12.5))+
  scale_y_continuous("Hour", breaks = seq(0,23,1),
                     limits = c(0,23),
                     labels = hoursLabel)+
  guides(size = guide_legend(ncol = 8))+
  theme_bw(base_size=15, base_family="Avenir")+
  theme(legend.position="bottom",
        legend.direction = "vertical")+
  labs(title = "Hours That Match Prescription Parameters",
       subtitle = paste(stationMetadata$STATION$NAME,": ",min(wx_df$Year)," - ",max(wx_df$Year),sep = ""))
rh_sub_Plot
```

```{r histPlot, include = TRUE, echo = FALSE, warning = FALSE, message = FALSE, dpi = 95, fig.width = widthPlots, fig.height = 6}
    wx_sub_countHours <- combinedWx %>%
      count(Month, Conditions) %>%
      group_by(Month) %>%
      mutate(Percent = n / sum(n))

histPlot <- ggplot(data = filter(wx_sub_countHours, Conditions == "In Prescription"),
                           aes(x = Month, y = Percent, fill = Conditions))+
          scale_y_continuous("Percent of Hours Matching Conditions (by month)",
                             labels = scales::percent)+
        geom_bar(color = "black", width = 1, stat = "identity", position="dodge")+
          scale_x_continuous(breaks = seq(1,12,1),
                             labels = c("JAN","FEB","MAR","APR","MAY","JUN","JUL","AUG","SEP","OCT","NOV","DEC"),
                             limits = c(0.5,12.5))+
        theme_bw(base_size=15, base_family="Avenir")+
          labs(title = "Percent of Hours That Match Prescription Parameters Per Month", subtitle = paste(stationMetadata$STATION$NAME,": ",min(wx_df$Year)," - ",max(wx_df$Year),sep = ""))+
        theme(legend.position="none")
      histPlot
```